Interoperable

### 2019-11-26 report/cloud-course-final-report/Article.tex
Update report

\section*{Design}
Interoperable framework will be a service which exists between developer and container runtimes. Our project aims to implement security checks across runtimes. The ultimate end goal will be to provide a means of lifecycle management of container runtimes in interoperable way. That is, a single script would be able to execute lifecyle commands independent of underlying container runtime.

@@

The underlying structure of the configuration files per runtime will be evaluated, as this is what we use in making each of these checks.
The interoperable framework will consist of scripts to be developed in Python.
The scripts serve as wrappers for functionality so that the end-user can run commands without caring which container runtime is the target container is running on.
Per the OCI standard, Docker, CRI-O, and containerd all use runc to implement low-level functionality. Thus, our intention is to leverage runc to create our interoperable framework. As seen in the above diagram, Docker implements its own image management and APIs for high level functionality on top of the container. Thus, understanding the interaction between the high level functionality and operations in runc is necessary in order to be able to implement the functionality in other frameworks.
\input{cis.tex}

@@

The minimum acceptance criteria for this course is to enable at least 5 benchmark checks on two different container runtimes. We target Docker and CRI-O as our primary focus. Our stretch goal criteria include ensuring the commands also work with containerd and be able to run the full suite of CIS Docker Benchmark checks from Chapters 5 (Container Runtime checks) and Chapter 4 (Container Images and Build File) on those runtimes.

In this section we demonstrate that we were able to perform more than 10 benchmarks over all container run-times (Docker, Containerd and Cri-o). 
\input{docker.tex}
\input{containerd.tex}
\input{crio.tex}
\input{frakti.tex}

>>>>

\section*{Design}
\input{design.tex}

@@

\input{implications.tex}
\input{cis.tex}

@@

In this section we demonstrate that we are able to perform more than 10 benchmarks over all container run-times (Docker, Containerd and Cri-o). For the sake of space, we only
mention about some of the benchmark implementation that were more challenging. For the other benchmarks, one can refer to tables that are located in appendix.
\input{docker.tex}
\input{containerd.tex}
\input{crio.tex}

\section*{Other benchmarks}
For the other benchmarks, interoperable application mainly leverages the fields that exist within the corresponding configuration files per container. For example,
to implement \textbf{5.4, 5.7, 5.8, 5.9, 5.12, 5.13, 5.14, 5.15, 5.16, 5.17, 5.18, 5.20 and 5.25} on Docker, we use Hostconfig.json file for a given container. This file
is created and stored per container in : \textit{/var/lib/docker/containers/} \textit{<container-id>/hostconfig.json}. To implement \textbf{5.3, 5.5, 5.21, 5.24} on docker, our application uses config.json under \textit{/run/containerd/io.containerd.runtime.v1.linux/moby/} \textit{<container-id>/config.json}.
\\
For crio, interoperable application implements \textbf{5.3, 5.4, 5.5, 5.7, 5.8, 5.9, 5.12, 5.13, 5.15, 5.16, 5.17, 5.20, 5.21, 5.24} using the config.json file per container. For crio this file is found from \textit{/var/lib/containers/storage/overlay-containers/}\textit{<container-id>/userdata/config.json}
\\

Containerd....

### 2019-11-26 report/cloud-course-final-report/abstract.tex
Update report

In this project, we will study the differences in popular runtimes Docker, containerd, and crio. Our focus will be on developing a service focused on ensuring that Center for Internet Security (CIS) Benchmarks for Docker are satisfied across other runtimes to ensure consistent application of security principles irrespective of container runtime differeces. Long term, the goal is to implement a lifecycle mangement solution that enables a common management framework for controlling containers across enviornments. By implementing a service to validate standard secuirty checks across runtimes, we intend to provide a Proof of Concept that such a common lifecycle management is possible.

>>>>

In this project, we study the differences in popular runtimes Docker, containerd, and crio. Our focus is on developing an interoperable application focused on ensuring that Center for Internet Security (CIS) Benchmarks are satisfied across runtimes to ensure consistent application of security principles irrespective of container runtime differences. By implementing an application, which can be exposed as a service to validate standard security checks across runtimes, we intend to provide a Proof of Concept that such a common lifecycle management is possible.

### 2019-11-26 report/cloud-course-final-report/cis5.tex
Update report

We implement following benchmarks:

@@

\subsubsection*{5.9 Do not share the host's network namespace (Scored)} This is potentially dangerous. It allows the container process to open low-numbered ports
like any other root process. It also allows the container to access network services like Dbus on the Docker host. Thus, a container process can potentially do unexpected things
such as shutting down the Docker host. You should not use this option.

>>>>

We mention following benchmarks for the sake of space. Other benchmarks that we implemented can be found from the appendix and their scopes/intentions can be evaluated from (https://www.cisecurity.org/benchmark/docker/):

@@

% \subsubsection*{5.9 Do not share the host's network namespace (Scored)} This is potentially dangerous. It allows the container process to open low-numbered ports
% like any other root process. It also allows the container to access network services like Dbus on the Docker host. Thus, a container process can potentially do unexpected things
% such as shutting down the Docker host. You should not use this option.

### 2019-11-26 report/cloud-course-final-report/crio.tex
Update report

\subsubsection*{Containerd}

Other platform that we evaluate interoperable application is Containerd  run-time. The process for implementing given benchmarks are pretty similar to Docker that is
mentioned above. Since different runtimes comes with different configuration files and corresponding structures, we state the implementation details as following.
First, we find target container's pid from \textit{/run/containerd/io.containerd.runtime.v2.task/default/}
\textit{<container-id>/init.pid}.
In order to issue \textbf{5.1 Do not disable AppArmor Profile} and \textbf{5.2 Verify SELinux security options} benchmarks on Containerd, interoperable application
uses procfs and corresponding pid for a container. Apparmor and SELinux are security attributes for a given process. 
These values are stored under \textit{/proc/<pid>/attr/apparmor/current} and \textit{/proc/<pid>/attr/selinux/current} respectively. 
By exposing these values, we are able to issue \textbf{5.1} and \textbf{5.2}.

Per container instance, configuration file is on containerd created under \textit{/run/containerd/io.containerd.runtime.v2.task/default/} \textit{/<container-id>/config.json} file.
From this file, we get \textbf{cgroup} path of a given container. Exposing this value also corresponds to \textbf{5.24} benchmark.

>>>>

\subsubsection*{Cri-o}

Other platform that we evaluate interoperable application is Cri-o  run-time. The process for implementing given benchmarks are pretty similar to Docker and Containerd.
Since different runtimes comes with different configuration files and corresponding structures, we state the implementation details as following.
First, we find target container's pid from its configuration file (i.e., specifically state.json) that is stored under \textit{/var/lib/containers/storage/overlay-containers/} \textit{<container-id>/userdata/state.json}
In order to issue \textbf{5.1 Do not disable AppArmor Profile} and \textbf{5.2 Verify SELinux security options} benchmarks on Containerd, interoperable application
uses procfs and corresponding pid for a container. Apparmor and SELinux are security attributes for a given process. 
These values are stored under \textit{/proc/<pid>/attr/apparmor/current} and \textit{/proc/<pid>/attr/selinux/current} respectively. 
By exposing these values, we are able to issue \textbf{5.1} and \textbf{5.2}.

Per container instance, configuration file is on crio created under \textit{//var/lib/containers/storage/overlay-containers/} \textit{<container-id>/userdata/config.json} file.
From this file, we get \textbf{cgroup} path of a given container. Exposing this value also corresponds to \textbf{5.24} benchmark.

### 2019-11-26 report/cloud-course-final-report/intro.tex
Update report

In this project, we will study the differences in popular runtimes Docker, containerd, and crio. Our focus will be on developing a service focused on ensuring that Center for Internet Security (CIS) Benchmarks for Docker are satisfied across other runtimes to ensure consistent application of security principles irrespective of container runtime differeces. Long term, the goal is to implement a lifecycle mangement solution that enables a common management framework for controlling containers across enviornments. By implementing a service to validate standard secuirty checks across runtimes, we intend to provide a Proof of Concept that such a common lifecycle management is possible.

\subsection{Vision and Goals}
Currently if someone wishes to launch an image in a container or perform any other lifecycle management functions on it, they must be sure that the scripts are configured correctly for the target container. For instance, launching images in Docker differs from doing so in CRI-O or containerd. This locks individuals and businesses into whichever container runtime they started with unless they invest the time required to edit the configuration and their scripts which holds the commands for target container.

Our short term goal for this project is to enable the set of Container Runtime tests run in the CIS Docker 1.13.0 Benchmark across any container runtime. These tests are specified in Chapter 5 of the document; example checks include restricting Linux Kernel capabilities within containers, limiting memory usage, and avoiding directly exposing the host devices to the containers. Publishing a minumum viable framework for this purpose will enable users to run their security checks using a single script across the most popular containers.

The ultimate goal is to develop an interoperable container runtime tool that allows user to perform common container lifecycle management functions among different runtimes using a single framework (e.g. start/stop execution, ps).

\subsection*{Users/Personas of the Project}
The intended user is a software developer who is developing, testing, and managing applications across containers running on different runtimes.

Example Use Case: A software developer would like to launch an image in CRI-O instead of Docker, because he realizes that CRI-O is more adaptable with Kubernetes, and using this capability will provide this application a lot more scalibility. Presently, he needs to deal with changing all the continous-integration scripts in order to be able to test and deploy his application on this new container runtime. With our interoperable framework in place, the developer is at least able to run security checks on the new container runtime without changing their scripts beyond specifying the new target container. In this way, the user's workflow is simplified and can apply a standard across runtimes with minimal effort.

\subsection*{Scope}
The runtimes in scope for capatibility for this project will be Docker, and CRI-O. containerd is considered a runtime in scope as a stretch goal.

This project aims to esnure that the framework implements commands that satisfy the CIS Docker 1.13.0 Benchmark related to Container Runtimes across our in-scope runtimes. In doing so, users will be enabled to run their security checks with a single script rather than requiring separate suites for each runtime. The MVP will be considered to be implementing select benchmarks in consultation with our mentor (highlighted in bold in the below list). Implementation of the full suite is a stretch goal.

>>>>

In this project, we study the differences in popular runtimes Docker, containerd, and crio. We propose an interoperable application focused on ensuring that Center for Internet Security (CIS) Benchmarks are satisfied across runtimes to ensure consistent application of security principles irrespective of container runtime differences. By implementing an application, which can be exposed as a service to validate standard security checks across runtimes, we intend to provide a Proof of Concept that such a common lifecycle management is possible. Minimum viable product for this project was to implement 5 CIS benchmarks from chapter 5 over at least two different container runtimes. However, we go way beyond the MVP and implement 23 Benchmark checks for docker, 20 for crio, and 16 for containerd. Detailed implementation for the benchmarks can be found in later sections and appendix.

\subsection{Vision and Goals}
Currently if someone wishes to launch an image in a container or perform any other lifecycle management functions on it, they must be sure that the scripts are configured correctly for the target container. For instance, launching images in Docker differs from doing so in crio or containerd. This locks individuals and businesses into whichever container runtime they started with unless they invest the time required to edit the configuration and their scripts which holds the commands for target container.

Our short term goal for this project is to enable the set of Container Runtime tests run in the CIS Docker 1.13.0 Benchmark across any container runtime. These tests are specified in Chapter 5 of the document; example checks include restricting Linux Kernel capabilities within containers, limiting memory usage, and avoiding directly exposing the host devices to the containers. Publishing a minimum viable framework for this purpose will enable users to run their security checks using a single application across the most popular containers.

\subsection*{Users/Personas of the Project}
The intended user is a software developer who is developing, testing or a security engineer who is managing applications and ensuring reliability across containers running on different runtimes.

Example Use Case: A software developer would like to launch an image in CRI-O instead of Docker, because he realizes that CRI-O is more adaptable with Kubernetes, and using this capability will provide this application a lot more scalability. Presently, he needs to deal with changing all the continous-integration scripts in order to be able to test and deploy his application on this new container runtime. With our interoperable framework in place, the developer is at least able to run security checks on the new container runtime with our application by specifying the new target container. In this way, the user's workflow is simplified and can apply a standard security checks across runtimes with minimal effort.

\subsection*{Scope}
The runtimes in scope for capability for this project will be Docker, and CRI-O. containerd is considered a runtime in scope as a stretch goal.

This project aims to ensure that the framework implements commands that satisfy the CIS Docker 1.13.0 Benchmark related to Container Runtimes across our in-scope runtimes. In doing so, users will be enabled to run their security checks with a single application rather than requiring separate suites for each runtime. The MVP is considered to be implementing at least 5 benchmarks in consultation with our mentor. Implementation of the full suite is a stretch goal.
